The Analogue Method for Precipitation Forecasting: Finding Better Analogue Situations at a Sub-Daily Time Step

### 2016-05-23 Moving temporal window - HESS/template.tex
Changes in structure.

The changes due to the introduction of a MTW was assessed first in regards to the analogy criteria improvement (Sect. \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect. \ref{sec:influence_scores}). Finally, attempts were made to reconstruct longer 24~h-total precipitations series (Sect. \ref{sec:attempts}).

\section{Study area and data}
\label{sec:data}

@@

\section{The moving time window (MTW) approach}
\label{sec:method}

@@

\section{Consequences of the archive reduction}

@@

\section{Influence on the analogy criteria}
\label{sec:influence_criteria}

\subsection{Changes in the atmospheric circulation analogy}

@@

\subsection{Influence of the weather situation}
\label{sec:influence_precip}

@@

\subsection{Seasonal effect}
\label{sec:seasonal_effect}

@@

\subsection{Changes in the moisture analogy}

@@

\section{Impact on performance scores}
\label{sec:influence_scores}

@@

\subsection{Improvement by precipitation classes}
\label{sec:improvement_CRPSS_precip_threshold}

@@

\subsection{Recalibrating the parameters}
\label{sec:recalibration}

@@

\subsection{Changes in sharpness and accuracy}

>>>>

The MTW is explained in Sect. \ref{sec:method}. As this method requires sub-daily time series, the available archive length is reduced compared to more common daily measurements, which has some consequences on the performance score (Sect. \ref{sec:archive_reduction}). The benefit of introducing a MTW was assessed first in regards to the analogy criteria improvement (Sect. \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect. \ref{sec:influence_scores}). Finally, attempts were made to reconstruct longer 24~h-total precipitations series (Sect. \ref{sec:attempts}).

\section{Data and method}

\subsection{Study area and data}
\label{sec:data}

@@

\subsection{The moving time window (MTW) approach}
\label{sec:method}

@@

\subsection{Consequences of the archive reduction}
\label{sec:archive_reduction}

@@

\section{Results and discussion}

\subsection{Influence on the analogy criteria}
\label{sec:influence_criteria}

\subsubsection{Changes in the atmospheric circulation analogy}

@@

\subsubsection{Influence of the weather situation}
\label{sec:influence_precip}

@@

\subsubsection{Seasonal effect}
\label{sec:seasonal_effect}

@@

\subsubsection{Changes in the moisture analogy}

@@

\subsection{Impact on performance scores}
\label{sec:influence_scores}

@@

\subsubsection{Improvement by precipitation classes}
\label{sec:improvement_CRPSS_precip_threshold}

@@

\subsubsection{Effect of recalibrating the parameters}
\label{sec:recalibration}

@@

\subsubsection{Changes in sharpness and accuracy}
